### 2021-11-10 documentos/pce.tex

\section{PCE Maps} 
\subsection{Quantum channels} % {{{ Quantum channels comprehend the most
general linear operations that a quantum system undergo independently of its
past~\cite{zimansbook,cirac}. To introduce their construction and properties,
first let us define several objects. We will denote Hilbert spaces as \hilbert
and $d$-dimensional Hilbert spaces as $\hilbert_d$. The set of bounded
operators over a Hilbert space \hilbert will be written as $\mcB(\hilbert)$,
the subset of density matrices as $\mcS(\hilbert)$, which is in turn a subset
of the so called trace-class operators $\mcT(\hilbert)$, for the finite
dimensional case, the one studied here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$
coincide~\cite{zimansbook}.

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. The trace preserving
property is needed to
send convex combinations of density matrices into the convex combination of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving property is required for the process $\mcE$ to be deterministic, this
is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete
positivity condition is needed to preserve positive semidefiniteness and handle
the non-local character of quantum theory. This is, with positivity of the map
$\mcE$ one has $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ with
$\Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
decimos que es una matriz de densidad}. In the other hand, complete positivity
of $\mcE$ reads $\id_k \otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where
$\omega$ is the Bell state
between the system and an ancilla with Hilbert space $\hilbert_k$\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }. Therefore,
complete positivity ensures that every positive semidefinite operator of any
extension of the system (where the quantum channel is now a local operation) is
mapped into positive semidefinite operators, trace preserving is automatically
fulfilled for all extensions if $\mcE$ is. Thus, any density matrix of a system
where $\mcE$ acts locally, is sent to a valid density matrix, this is the
substance of complete positivity.

>>>>

\section{PCE Maps} 
\subsection{Quantum channels} % {{{
Quantum channels comprehend the most general linear operations that a quantum
system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
their construction and properties, first let us define several objects. We will
denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
$\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
be written as $\mcB(\hilbert)$.
%, the subset of density matrices as
%$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
%operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
%here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. The first one is needed to
send convex combinations of density matrices into the convex combinations of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving is required for the process $\mcE$ to be deterministic, this
is $\tr\mcE[\rho]=\tr \rho =1$ for any density matrix $\rho$, \ie{} the process $\mcE$ will
happen with probability equal to one. The complete
\subsection{Quantum channels} % {{{ Quantum channels comprehend the most
general linear operations that a quantum system undergo independently of its
past~\cite{zimansbook,cirac}. To introduce their construction and properties,
first let us define several objects. We will denote Hilbert spaces as \hilbert
and $d$-dimensional Hilbert spaces as $\hilbert_d$. The set of bounded
operators over a Hilbert space \hilbert will be written as $\mcB(\hilbert)$,
the subset of density matrices as $\mcS(\hilbert)$, which is in turn a subset
of the so called trace-class operators $\mcT(\hilbert)$, for the finite
dimensional case, the one studied here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$
coincide~\cite{zimansbook}.

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. The trace preserving
property is needed to
send convex combinations of density matrices into the convex combination of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving property is required for the process $\mcE$ to be deterministic, this
is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete
>>>>>>> 50430f9b3813da4a6f9b09d9b473cf9477afefd3
positivity condition is needed to preserve positive semidefiniteness and handle
the non-local character of quantum theory. This is, with positivity of the map
$\mcE$ one has $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ with
$\Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
decimos que es una matriz de densidad}. In the other hand, complete positivity
of $\mcE$ reads $\id_k \otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where
$\omega$ is the Bell state
between the system and an ancilla with Hilbert space $\hilbert_k$\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }. Therefore,
complete positivity ensures that every positive semidefinite operator of any
extension of the system (where the quantum channel is now a local operation) is
mapped into positive semidefinite operators, trace preserving is automatically
fulfilled for all extensions if $\mcE$ is. Thus, any density matrix of a system
where $\mcE$ acts locally, is sent to a valid density matrix, this is the
substance of complete positivity.
